Clustering Beat-Chroma Patterns\\ in a Large Music Database

### 2010-03-24 Paper/Paper.tex
clustering intro slightly improved

\subsection{Cluster}
Visualizing a codebook is half of the story, we also want to understand
clusters, \ie the patterns from actual song that
surround a given centroid (codeword). Unsurprisingly, real patterns are
noisier than codes. However, centroids seem to capture important aspects
of the patterns. We could compare the centroids with the result of
a lowpass filtering. In Figure \ref{fig:cluster} we show elements of the same
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.

>>>>

\subsection{Cluster}
Clusters are formed around a centroid (codeword) by all patterns closer
to that codeword than any other. Since the centroid is somewhat an
average of those patterns, the latter tend to be noisier. Hence, codewords
can be seen as the output of a lowpass filtering mecanism.
In Figure \ref{fig:cluster} we show elements of one given
cluster, and in Figure \ref{fig:cluster_diff}, we emphasize the difference
with the centroid. We hope for the difference to look uniformly random,
the result seems to fit that assumption.
